\newglossaryentry{autonomous}
{%
	name={autonomous},
	description={Autonomous control implies satisfactory performance under
	significant uncertainties in the environment and the ability to
	compensate for system failures without external intervention.}
}

\newglossaryentry{automated}
{%
	name={automated},
	description={An automated function is operated by a machine}
}

\newglossaryentry{self-driving}
{%
	name={self-driving},
	description={Self-driving vehicles are cars or trucks in which human
	drivers are never required to take control to safely operate the
	vehicle. Also known as autonomous or “driverless” cars}
}

\newglossaryentry{driverless}
{%
	name={driverless},
	description={A vehicle that does not have a human driver neither on
	board or through remote communication. Often used for self-driving or
	autonomous vehicles.}
}

\newglossaryentry{vehicle}
{%
	name={vehicle},
	description={A vehicle is a machine that transports people or cargo.}
}

\newglossaryentry{SAE}
{%
	name={SAE},
	description={Society of Automotive Engineers}
}

\newglossaryentry{SAE0}
{%
	name={SAE 0},
	description={Automation level. Automated system issues warnings and may
	momentarily intervene but has no sustained vehicle control.}
}

\newglossaryentry{SAE1}
{%
	name={SAE 1},
	description={Automation level. The driver and the automated system share
	control of the vehicle. Examples are Adaptive Cruise Control (ACC)}
}

\newglossaryentry{AdaptiveCruiseControl}
{%
	name={Adaptive Cruise Control},
	description={Not only maintains a set speed}
}

\newglossaryentry{ParkingAssistance}
{%
	name={Parking Assistance},
	description={Automatic parking is an autonomous car-maneuvering system
	that moves a vehicle from a traffic lane into a parking spot to perform
	parallel}
}

\newglossaryentry{LaneKeepingAssistance}
{%
	name={Lane Keeping Assistance},
	description={Automatically steers the vehicle back into its lane if it
	begins to drift out of it.}
}

\newglossaryentry{automatic}
{%
	name={automatic},
	description={Something that is automated.}
}

\newglossaryentry{automatically}
{%
	name={automatically},
	description={In an automated way.}
}

\newglossaryentry{SAE2}
{%
	name={SAE 2},
	description={Automation level. The automated system takes full control
	of the vehicle (accelerating)}
}

\newglossaryentry{SAE3}
{%
	name={SAE 3},
	description={Automation level. The driver can safely turn their
	attention away from the driving tasks}
}

\newglossaryentry{SAE4}
{%
	name={SAE 4},
	description={Automation level. As SAE 3}
}

\newglossaryentry{SAE5}
{%
	name={SAE 5},
	description={Automation level. No human intervention is required at all.
	An example would be a robotic taxi.}
}

\newglossaryentry{disengagement}
{%
	name={disengagement},
	description={An event when the automated system is turned off either
	because of an error}
}

\newglossaryentry{milesPerDisengagement}
{%
	name={miles per disengagement},
	description={The average distance driven between turning the system on
	(again) and the first disengagement. A metric that is used to assess the
	progress of automated vehicles.}
}

\newglossaryentry{authorized}
{%
	name={authorized},
	description={Having official permission or approval to operate.}
}

\newglossaryentry{stakeholder}
{%
	name={stakeholder},
	description={Anyone interested in the project.}
}

\newglossaryentry{HealthAndSafetyRegulations}
{%
	name={health\&safety regulations},
	description={The set of rules the Health\&Safety Department devised in
	order to ensure that nothing in the office park is hazardous to the
	personnel.}
}

\newglossaryentry{HealthAndSafetyDepartment}
{%
	name={Health\&Safety Department},
	description={A group at our company responsible for analyzing the
	potential health and safety risks of our products and forming rules and
	regulations to make sure these risks are averted.}
}

\newglossaryentry{monitor}
{%
	name={monitor},
	description={To regularly check the environment in order to discover
	changes.}
}

\newglossaryentry{sensor}
{%
	name={sensor},
	description={A device whose purpose is to detect the changes of its
	environment and inform computer logic.}
}

\newglossaryentry{station}
{%
	name={station},
	description={A dedicated place inside the office park for the storage
	and maintenance the buses when they are not in service.}
}

\newglossaryentry{lunchBreak}
{%
	name={lunch break},
	description={A specified period of time during the day when personnel
	may have lunch. It is a 1.5 hour long break between 12:00 and 13:30.}
}

\newglossaryentry{overcrowding}
{%
	name={overcrowding},
	description={The event that occurs when the number of passengers exceeds
	the bus's capacity and weight regulation. This can not only prevent the
	adequate operation of the bus but it also poses a safety risk.}
}

\newglossaryentry{specification}
{%
	name={specification},
	description={A document that describes the behaviour of the system.}
}

\newglossaryentry{blackBox}
{%
	name={black box},
	description={A machine that records and stores information about the
	vehicle during its operation with the purpose of providing information
	regarding the chain of events leading up to an accident.}
}

\newglossaryentry{non-criticalFailure}
{%
	name={non-critical failure},
	description={An error or condition that decreases the performance of the
	system but can be tolerated until fixed.}
}

\newglossaryentry{technicalProblem}
{%
	name={technical problem},
	description={A problem with the bus’s operation involving one of its
	automotive components. A technical problem does not necessarily mean the
	bus is unable to function.}
}

\newglossaryentry{criticalFailure}
{%
	name={critical failure},
	description={A breakdown caused by the failure of a critical component
	of the bus. The bus is unable to function according to its
	specifications.}
}

\newglossaryentry{route}
{%
	name={route},
	description={The way a vehicle follows in order to reach the required
	destination.}
}

\newglossaryentry{request}
{%
	name={request},
	description={A notification used to indicate the office worker's
	intentions to get to certain offices.}
}

\newglossaryentry{terminal}
{%
	name={terminal},
	description={An electronic equipment equipped with a touch screen used
	for transportation requests and communicating with the computer system
	of the buses.}
}

\newglossaryentry{traffic}
{%
	name={traffic},
	description={The movement of vehicles}
}

\newglossaryentry{mobileApplication}
{%
	name={mobile application},
	description={A software program used by the registered users. It gives
	users the ability to publish their transportation requests in advance.}
}

\newglossaryentry{transportation}
{%
	name={transportation},
	description={The use of a vehicle for getting people or goods from one
	place to another.}
}

\newglossaryentry{site}
{%
	name={site},
	description={The office park.}
}
