\newglossaryentry{stakeholder}
{%
	name={stakeholder},
	description={Anyone interested in the project.}
}

\newglossaryentry{health and safety regulations}
{%
	name={health and safety regulations},
	description={The set of rules the Health and Safety Department devised in order to ensure that nothing in the office park is hazardous to the personnel.}
}

\newglossaryentry{Health and Safety Department}
{%
	name={Health and Safety Department},
	description={A group at our company responsible for analyzing the potential health and safety risks of our products and forming rules and regulations to make sure these risks are averted.}
}

\newglossaryentry{monitor}
{%
	name={monitor},
	description={To regularly check the environment in order to discover changes.}
}

\newglossaryentry{sensor}
{%
	name={sensor},
	description={A device whose purpose is to detect the changes of its environment and inform computer logic.}
}

\newglossaryentry{station}
{%
	name={station},
	description={A dedicated place inside the office park for the storage and maintenance the buses when they are not in service.}
}

\newglossaryentry{lunch break}
{%
	name={lunch break},
	description={A specified period of time during the day when personnel may have lunch. It is a 1.5 hour long break between 12:00 and 13:30.}
}

\newglossaryentry{overcrowding}
{%
	name={overcrowding},
	description={The event that occurs when the number of passengers exceeds the bus's capacity and weight regulation. This can not only prevent the adequate operation of the bus but it also poses a safety risk.}
}

\newglossaryentry{specification}
{%
	name={specification},
	description={A document that describes the behaviour of the system.}
}

\newglossaryentry{black box}
{%
	name={black box},
	description={A machine that records and stores information about the vehicle during its operation with the purpose of providing information regarding the chain of events leading up to an accident.}
}

\newglossaryentry{non-critical failure}
{%
	name={non-critical failure},
	description={An error or condition that decreases the performance of the system but can be tolerated until fixed.}
}

\newglossaryentry{technical problem}
{%
	name={technical problem},
	description={A problem with the bus’s operation involving one of its automotive components. A technical problem does not necessarily mean the bus is unable to function.}
}

\newglossaryentry{critical failure}
{%
	name={critical failure},
	description={A breakdown caused by the failure of a critical component of the bus. The bus is unable to function according to its specifications.}
}

\newglossaryentry{route}
{%
	name={route},
	description={The way a vehicle follows in order to reach the required destination.}
}

\newglossaryentry{request}
{%
	name={request},
	description={A notification used to indicate the office worker's intentions to get to certain offices.}
}

\newglossaryentry{terminal}
{%
	name={terminal},
	description={An electronic equipment equipped with a touch screen used for transportation requests and communicating with the computer system of the buses.}
}

\newglossaryentry{traffic}
{%
	name={traffic},
	description={The movement of vehicles}
}

\newglossaryentry{mobile application}
{%
	name={mobile application},
	description={A software program used by the registered users. It gives users the ability to publish their transportation requests in advance.}
}

\newglossaryentry{transportation}
{%
	name={transportation},
	description={The use of a vehicle for getting people or goods from one place to another.}
}

\newglossaryentry{site}
{%
	name={site},
	description={The office park.}
}

\newglossaryentry{Automated Passenger Counter}
{%
	name={Automated Passenger Counter},
	description={There is an electronic device on vehicles which accurately records the numbers of people getting on and off at each station.}
}

\newglossaryentry{Intelligent Intersection Control}
{%
	name={Intelligent Intersection Control},
	description={A control unit which automatically controls pedestrian and vehicular traffic lights based on information gathered by various sensors and communication with a central traffic management system.}
}

\newglossaryentry{APC}
{%
	name={APC},
	description={Automated Passenger Counter}
}

\newglossaryentry{IIC}
{%
	name={IIC},
	description={Intelligent Intersection Control}
}

\newglossaryentry{intersection control unit}
{%
	name={intersection control unit},
	description={It is a computerized control and coordination unit in traffic control systems which changes traffic lights (red}
}

\newglossaryentry{intersection}
{%
	name={intersection},
	description={The place where two or more roads cross each other.}
}

\newglossaryentry{T-intersection}
{%
	name={T-intersection},
	description={A road coming from the west meets a north-to-south road.}
}

\newglossaryentry{pedestrian control button}
{%
	name={pedestrian control button},
	description={A button at intersections that triggers a change of the traffic light to green upon the pedestrians’ demand.}
}

\newglossaryentry{central traffic management system}
{%
	name={central traffic management system},
	description={A system aimed to monitor and control traffic based on collected information}
}

\newglossaryentry{Traffic and Route Planning}
{%
	name={Traffic and Route Planning},
	description={A program which computes the optimal route from one place to another by minimizing travel distance and/or travel time.}
}

\newglossaryentry{TRP}
{%
	name={TRP},
	description={Traffic and Route Planning}
}

\newglossaryentry{passenger counter}
{%
	name={passenger counter},
	description={A device which automatically monitors the number of passengers boarding and alighting.}
}

\newglossaryentry{passenger monitoring module}
{%
	name={passenger monitoring module},
	description={A device which reports current passengers’ status to central traffic management and route planning services.}
}

\newglossaryentry{call button}
{%
	name={call button},
	description={pedestrian control button}
}

\newglossaryentry{optimizer}
{%
	name={optimizer},
	description={A part of the service route planner responsible for optimization to achieve minimal total passenger request–transport arrival delay.}
}

\newglossaryentry{maintenance manager}
{%
	name={maintenance manager},
	description={The part of the service route planner which ensures that vehicles undergo the required amount of maintenance and recharging so that they can safely and reliably transport passengers.}
}

\newglossaryentry{telemetry}
{%
	name={telemetry},
	description={The collection of data at remote places and their automatic transmission to receiving equipment for monitoring.}
}

\newglossaryentry{congestion prediction}
{%
	name={congestion prediction},
	description={The capability to predict a condition of transport that is characterized by slower speeds}
}

\newglossaryentry{demand prediction}
{%
	name={demand prediction},
	description={The prediction of upcoming intentions for transportation. Shall be taken into account the special events manually provided by operators and the historical data on aggregated personal travel requests.}
}

\newglossaryentry{crossing telemetry data}
{%
	name={crossing telemetry data},
	description={The collection of data remotely collected at intersections.}
}

